The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-07-25 paper.tex
wip

However in many cases the study of CMB foregrounds is scientifically interesting in its own right.
Measurements of dust-correlated anomalous microwave emission \citep{1997ApJ...486L..23L} led to the
discovery of spinning dust emission \citep{1998ApJ...508..157D}. Thomson scattering in the IGM
attenuates the CMB spectrum, but the optical depth implies a mean redshift to the Epoch of
Reionization (EoR) of $8.8^{+1.7}_{-1.4}$ \citep{2016A&A...594A..13P}.  The thermal
Sunyaev-Zel'dovich effect \citep{1970CoASP...2...66S, 1972CoASP...4..173S} has been used to discover
new galaxy clusters \citep{2010ApJ...722.1180V} and measure the distance to galaxy clusters when
combined with X-ray measurements \citep{2006ApJ...647...25B}.

\todo{kinetic SZ effect puts an upper limit on the duration of reionization}

At redshifts $20 \gtrsim z \gtrsim 7$ the 21 cm hyperfine structure line of neutral hydrogen is
expected to produce a 10 to 100 mK perturbation in the CMB spectrum \citep{2006PhR...433..181F,
2012RPPh...75h6901P}. The amplitude of this perturbation on a given line-of-sight is a function of
the neutral fraction of hydrogen, the baryon overdensity, the spin temperature relative to the CMB
temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.

\todo{discuss 21cmmc ionizing efficiency, photon mean free path, minimum halo mass}
\todo{discuss what can be learned from global experiments}

The spatial power spectrum of this perturbation is expected to be dominated
by inhomogeneous heating of the IGM at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing
ionized bubbles during the EoR at $z\sim 7$ \todo{citation}.

@@

\citet{2011A&A...525A.138G}

\todo{TGSS, MSSS, GLEAM}

@@

\begin{figure*}[ht]
    \plotone{maps/rgb-map-small}
    \caption{three color map}
    \label{fig:rgb}
\end{figure*}

>>>>

However in many cases the study of CMB foregrounds is scientifically interesting in its own right.
Measurements of dust-correlated anomalous microwave emission \citep{1997ApJ...486L..23L} led to the
discovery of spinning dust emission \citep{1998ApJ...508..157D}. Thomson scattering in the IGM
attenuates the CMB spectrum, but the optical depth implies a mean redshift to the Epoch of
Reionization (EoR) of $z_r = 8.8^{+1.7}_{-1.4}$ \citep{2016A&A...594A..13P}.  The thermal
Sunyaev-Zel'dovich effect \citep{1970CoASP...2...66S, 1972CoASP...4..173S} has been used to discover
new galaxy clusters \citep{2010ApJ...722.1180V} and measure the distance to galaxy clusters when
combined with X-ray measurements \citep{2006ApJ...647...25B}. The kinetic Sunyaev-Zel'dovich effect
has been used to constrain the duration of reionization $\Delta z_r \le 4.4$
\citep{2012ApJ...756...65Z}.

At redshifts $20 \gtrsim z \gtrsim 7$ the 21 cm hyperfine structure line of neutral hydrogen is
expected to produce a 10 to 100 mK perturbation in the CMB spectrum \citep{2006PhR...433..181F,
2012RPPh...75h6901P}. The amplitude of this perturbation on a given line-of-sight is a function of
the neutral fraction of hydrogen, the baryon overdensity, the spin temperature relative to the CMB
temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.  The spatial
power spectrum of this perturbation is expected to be dominated by inhomogeneous heating of the IGM
at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing ionized bubbles during the EoR at $z\sim
7$ where a detection can constrain the ionizing efficiency of early galaxies, UV photon
mean-free-path, and the minimum halo mass that can support star formation
\citep{2015MNRAS.449.4246G}.

@@

Recently a host of new low-frequency sky surveys have been conducted including MSSS
\citep{2015A&A...582A.123H}, GLEAM \citep{2015PASA...32...25W}, and TGSS
\citep{2017A&A...598A..78I}. However, the primary data product generated by these surveys is a
catalog of radio sources. Surveys that capture the diffuse emission include at 45 MHz, where
\citet{2011A&A...525A.138G} produced a map of the sky with 5$^\circ$ resolution, and the LWA1 Low
Frequency Sky Survey \citet{2017MNRAS.469.4537D}, which covers a range of frequencies between 35 MHz
and 80 MHz with resolution betwen 4.5$^\circ$ and 2$^\circ$.

In this paper we will present a series of new low-frequency maps of the sky between 36.528 Mhz and
73.152 Mhz, capturing the full sky visible from the Owens Valley Radio Observatory (OVRO) with
angular resolution of roughly 10'. These maps are generated using $m$-mode analysis imaging -- a new
imaging technique for transit telescopes.

@@

\begin{figure*}[ht]
    \plotone{maps/2017-04-20-rgb-map-smaller}
    \caption{three color map}
    \label{fig:rgb}
\end{figure*}
